%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - tighter for single page
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{#2} & #3 \\
      \textit{\small#4} & \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]} % Adjust leftmargin for bullet alignment
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
   \textbf{\Huge \scshape Tan Hiok Kuek} \\
    \vspace{2mm}
    \large Currently interested in System Design \\
    \vspace{1mm}
    +65 87966816 $|$
    \href{mailto:ernest.tanhk@gmail.com}{\underline{\textcolor{blue}{ernest.tanhk@gmail.com}}} $|$
    \href{https://hiok.dev}{\underline{\textcolor{blue}{hiok.dev}}} $|$
    \href{https://www.linkedin.com/in/hiokkuek}{\underline{\textcolor{blue}{Linkedin}}} $|$
    \href{https://github.com/HiokKuek}{\underline{\textcolor{blue}{Github}}}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{}{Aug 2024 -- Jan 2028}
      {Bachelor of Computing in Computer Science (Cumulative GPA 4.64)}
      \resumeItemListStart
        \resumeItem{Ngee Ann Kongsi Scholarship for AY 25/26}
        \resumeItem{Peer Mentor for Science \& Technology Scholars}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Work Experience-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Teaching Assistant (CS2030S)}{-- NUS School of Computing}
      {Jan 2026 -- Present}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Facilitating lab sessions for \textbf{Programming Methodology II}, covering \textbf{Object-Oriented Programming} and \textbf{Functional Programming} abstractions in Java (Monads, Functors, etc.).}
        \resumeItem{Mentoring 20+ students in developing robust software designs, focusing on \textbf{CS fundamentals}, recursion, and type systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{-- NUS-NCS Cybersecurity Lab}
      {Aug 2024 -- Aug 2025}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Sole frontend engineer owning architecture, performance, and delivery for a production platform used by \textbf{10,000+ users}.}
        \resumeItem{Reduced AWS Cost by \textbf{50\% (\$200/day to \$100/day)} through scalable archictecture and automation using \textbf{cloudwatch}.}
        \resumeItem{Built backend AI workflows using \textbf{Python and modern LLM orchestration tool} to detect phishing emails.}
        \resumeItem{Designed customer-driven dashboards enabling comparison between workflows, activity tracking and decision-critical insights.}
        \resumeItem{Built cross-platform \textbf{browser extension} bundled with a \textbf{native host}, that supports \textbf{on-premise} email phishing detection.}
        \resumeItem{Stabilised production systems by migrating AWS infrastructure over to Terraform under tight deadlines.}
    
      \resumeItemListEnd

    \resumeSubheading
      {Deputy Head Ops and Security Officer}{-- Singapore Armed Forces}
      {Jan 2023 -- Nov 2023}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Managed operations and security for a unit of \textbf{300+ personnel}, coordinating complex training logistics and data security.}
        \resumeItem{Recognized with multiple honors including \textbf{Sword of Merit} and \textbf{Commanding Officer’s Coin} for operational excellence.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECT EXPERIENCE-----------
\section{TECHNICAL PROJECTS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Agentic Social Media Content Generator}{-- AI Agents \& LLM Orchestration}
      {Sep 2025}{}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Engineered an \textbf{autonomous AI agent pipeline} using \textbf{LangSmith}, \textbf{GPT-4}, and \textbf{Claude} to scrape Reddit data, perform sentiment analysis, and generate creative scripts with automated quality checks.}
        \resumeItem{Implemented comprehensive tracing and monitoring to optimize LLM cost and performance for production-ready agents.}
      \resumeItemListEnd
      
      \resumeSubheading
      {HomeLab Infrastructure}{-- Personal Server \& Automation}
      {Jul 2025}{}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Architected a Linux-based home server environment with \textbf{Docker} for containerized services, managing automated backups and private cloud storage.}
        \resumeItem{Deployed secure remote access using \textbf{Cloudflare Tunnels} and managed network traffic for self-hosted instances.}
      \resumeItemListEnd


    \resumeSubheading
      {Tanbucha}{-- E-commerce Platform}
      {May 2025}{\href{https://tanbucha.com}{\underline{\textcolor{blue}{tanbucha.com}}}}
      \resumeItemListStart
        \resumeItem{Built responsive e-commerce platform with \textbf{Next.js} and \textbf{TypeScript}, implementing mobile-first design patterns.}
        \resumeItem{Integrated \textbf{Stripe API} for payment processing and \textbf{EmailJS} for automated customer notifications.}
        \resumeItem{Achieved \textbf{50+ organic visitors} and \textbf{100+ sales} through SEO optimization and performance tuning.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS-----------
\section{HONORS \& TECHNICAL COMPETITIONS}
\begin{tabularx}{\textwidth}{X X X}
  {\bfseries\large$\cdot$} NUS Hackers Hack\&Roll (1st) & {\bfseries\large$\cdot$} SplashAwards 2023 (1st) & {\bfseries\large$\cdot$} SUTD WhatTheHacks 2023 (1st) \\
  {\bfseries\large$\cdot$} CloudHacks 2023 (1st) & {\bfseries\large$\cdot$} GroundZero 2024 (Finals) & {\bfseries\large$\cdot$} NUS CHS Case Comp (Finals) \\
\end{tabularx}


%-----------SKILLS & INTERESTS-----------
\section{SKILLS \& INTERESTS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
    \textbf{Languages}{: Python {\bfseries\large$\cdot$} Java {\bfseries\large$\cdot$} Javascript/TypeScript/HTML/CSS (TypeScript) {\bfseries\large$\cdot$} SQL}} \\
    \vspace{1mm}
    \textbf{Tools \& Frameworks}{: React, Next.js, Plasmo {\bfseries\large$\cdot$} Flask {\bfseries\large$\cdot$} OpenAI, LangChain, LangSmith {\bfseries\large$\cdot$} Docker, Terraform {\bfseries\large$\cdot$} PostgreSQL } \\
    \vspace{1mm}
    \textbf{Certifications}{: \href{https://www.credly.com/badges/bdd6f6cb-d507-41a4-954f-b4cfb2d3a049/public_url}{\underline{\textcolor{blue}{AWS Certified Solutions Architect - Associate (SAA-C03)}}}} \\
    \vspace{1mm}
    \textbf{Interests}{: Applied AI {\bfseries\large$\cdot$} Machine Learning {\bfseries\large$\cdot$} Full-Stack Development {\bfseries\large$\cdot$} Cloud Computing} \\
    }
 \end{itemize}
 \begin{center}
\end{center}


\end{document}